Automated Topic Naming

### 2011-08-23 ese/ese.tex
updating pg timeline plot

%FAT
%\newpage

@@

%FAT we can remove this
%\balance
%LFAT
\newpage
\begin{quotation}
\small \noindent \textsf{
integrity, security,
interoperability, testability, maintainability, traceability,
accuracy, modifiability, understandability, availability, modularity,
usability, correctness, performance, verifiability, efficiency,
portability, flexibility, reliability.
}
\end{quotation}

@@

MaxDB 7.500 & Named Topics   & 281 & 125 & 328 \\ % these numbers are
				% slightly different solely because
				% we're counting empty topics
				% maxdb has 80 empty topics
 & Unnamed Topics & 219  & 375 &  172  \\
 & Total  Topics  & 500 & 500 & 500 \\
\midrule
MySQL 3.23  & Named Topics   & 524 & 273 & 773 \\
  & Unnamed Topics & 476 & 727 & 227 \\
  & Total  Topics  & 1000 & 1000 & 1000 \\

\todo{update with PGSQL}
\bottomrule
\end{tabular}
	\caption{Automatic topic labelling for MaxDB and MySQL}% \todo[inline]{this stupid table is before table 1}}
	\label{tbl:wordlist}

\end{table}

% was best performing
For \textsf{exp1} the labels with the most topics
were
%labels, those with the most topics, 
\emph{correctness} (182 topics) and \emph{testability} (121). 
We did not see many results for \emph{usability} or \emph{accuracy}, which were associated with fewer than ten topics. 
We also looked for correlations between our labels: excluding double matches (self-correlation), our highest co-occurring terms were \emph{verifiability}
with \emph{traceability}, and \emph{testability} with \emph{correctness} (76 and 62 matches, respectively).
% See the following sections for our error analysis.

@@

%FAT

%\newpage

%\subsection{Timeline analysis}
Figures \ref{fig:mysql-timeline} and \ref{fig:maxdb-timeline} show the
temporal patterns of NFR frequencies.
%NEIL- I think this (below) is just confusing, although maybe important to note.
% based on the manually annotated
%topics, although this visualization can be generated from the
%results of labelled topic extraction.
There are two measures represented. 
One, the relative frequency, shown in the grey histogram boxes, represents the number of topics with that NFR in that period, 
relative to the maximum number of topics assigned to that NFR. 
For example, in Figure \ref{fig:mysql-timeline} we see a spike in \emph{portability} and \emph{functionality} frequency in September 2002.
The second, absolute frequency, is shown using cell intensity, and compares the number of topics labelled with that NFR per period 
relative to the maximum number of labelled topics overall. 
For instance, Figure \ref{fig:mysql-timeline} shows that the NFRs
\emph{functionality}, \emph{portability} and \emph{maintainability}
contain more labelled topics, since these NFRs have been more
intensely shaded; 
one interesting stream is \emph{efficiency} which shows periodic
activity, does this suggest that once maybe efficiency related changes
have longer lasting effects?
The topmost row in each diagram lists historical events for that project (such as a release). 
%We refer to these occurrences in the discussion which follows.

\begin{figure*}[t]
\centering
\subfloat[MySQL 3.23]{
\includegraphics[width=\textwidth]{figures/mysql-timeline.png}
\label{fig:mysql-timeline}				 
}

\subfloat[MaxDB 7.500]{					
\includegraphics[width=\textwidth]{figures/maxdb-timeline.png}
\label{fig:maxdb-timeline}
}
\subfloat[PostgreSQL 7.2]{					
\includegraphics[width=\textwidth]{figures/pgsql-timeline}
\label{fig:pgsql-timeline}
}
	\caption[]{NFR label per period. Each cell represents a 30-day period. %Numbers represent number of topics in that period labelled with that NFR. 
	Grid cell intensity (saturation) is mapped to label frequency
	relative to the largest label count of \emph{all} NFRs. Grey
	histogram bars indicate label frequency relative to that
	particular NFR's largest label count. Dashed vertical lines
	relate a project milestone (\emph{*Key events*}) to our topic windows. 
% \todo[inline]{better discussion}
}
\label{fig:timelines}
\end{figure*}

@@

%LFAT
\balance
\newpage
\subsection{Do Projects Differ in their Relative  Topic Interest?}
%\subsubsection{Do  projects differ in their relative  topic interest?}
%\noindent\textbf{2. Do  projects differ in their relative  topic interest?} ---
Yes. MySQL 3.23 had proportionally more
topics labelled \emph{functionality}, while MaxDB had proportionally more
\emph{efficiency} related topics. MaxDB was a very mature release ``donated'' to the open-source community, 
whereas MySQL was in its relative infancy, and	
security problems were more common (security is a component of \emph{functionality} in the ISO9126 model). 
In both cases \emph{portability} was a constant maintenance concern and was prevalent throughout the lifetime of the projects. It may surprise developers
how often portability arises as a concern.
%On one hand, this analysis is unsurprising; on the other hand, it provides confirmation that our approach identifies actual patterns.
%\subsection{Summary}

@@

%FAT
%\newpage
\subsection{Summary of Techniques}
While an unsupervised technique such as LDA is appealing in its lack of human intervention, and thus lower effort, 
supervised learners have the advantage of domain knowledge, which typically means improved results. 
% NEIL - we got criticized for making it sound like this is the obvious thing to do... and then why do you need a learner?
%Our manual annotations were fairly quick to do, taking only a few minutes per 30 day period. 
Creating annotated topics (i.e., manual labels) for training is painstaking, but with a suitably representative set of topics, the effort is acceptable. To
annotate \emph{all} topics took us approximately 20 hours per project, but we estimate only 10\% of the topics need annotation to produce useful results.

@@

%LFAT
\balance
\newpage

>>>>

@@

\begin{quotation}
\small \noindent \textsf{
integrity, security,
interoperability, testability, maintainability, traceability,
accuracy, modifiability, understandability, availability, modularity,
usability, correctness, performance, verifiability, efficiency,
portability, flexibility, reliability.
}
\end{quotation}

@@

MaxDB 7.500 & Named Topics   & 281 & 125 & 328 \\ % these numbers are
				% slightly different solely because
				% we're counting empty topics
				% maxdb has 80 empty topics
 & Unnamed Topics & 219  & 375 &  172  \\
 & Total  Topics  & 500 & 500 & 500 \\
\midrule
MySQL 3.23  & Named Topics   & 524 & 273 & 773 \\
  & Unnamed Topics & 476 & 727 & 227 \\
  & Total  Topics  & 1000 & 1000 & 1000 \\
\midrule
PgSQL 3.23  & Named Topics   & - & - & - \\
  & Unnamed Topics & - & - & - \\
  & Total  Topics  & - & - & - \\

\bottomrule
\end{tabular}
	\caption{Automatic topic labelling for MaxDB and MySQL}% \todo[inline]{this stupid table is before table 1}}
	\label{tbl:wordlist}

\end{table}
\todo{update with PGSQL}
% was best performing
For \textsf{exp1} the labels with the most topics
were
%labels, those with the most topics, 
\emph{correctness} (182 topics) and \emph{testability} (121). 
We did not see many results for \emph{usability} or \emph{accuracy}, which were associated with fewer than ten topics. 
We also looked for correlations between our labels: excluding double matches (self-correlation), our highest co-occurring terms were \emph{verifiability}
with \emph{traceability}, and \emph{testability} with \emph{correctness} (76 and 62 matches, respectively).
% See the following sections for our error analysis.

@@

%\subsection{Timeline analysis}
Figures \ref{fig:mysql-timeline} and \ref{fig:maxdb-timeline} and \ref{fig:pgsql-timeline} show the
temporal patterns of NFR frequencies.
%NEIL- I think this (below) is just confusing, although maybe important to note.
% based on the manually annotated
%topics, although this visualization can be generated from the
%results of labelled topic extraction.
There are two measures represented. 
One, the relative frequency, shown in the grey histogram boxes, represents the number of topics with that NFR in that period, 
relative to the maximum number of topics assigned to that NFR. 
For example, in Figure \ref{fig:mysql-timeline} we see a spike in \emph{portability} and \emph{functionality} frequency in September 2002.
The second, absolute frequency, is shown using cell intensity, and compares the number of topics labelled with that NFR per period 
relative to the maximum number of labelled topics overall. 
For instance, Figure \ref{fig:mysql-timeline} shows that the NFRs
\emph{functionality}, \emph{portability} and \emph{maintainability}
contain more labelled topics, since these NFRs have been more
intensely shaded; 
one interesting stream is \emph{efficiency} which shows periodic
activity, does this suggest that once maybe efficiency related changes
have longer lasting effects?
The topmost row in each diagram lists historical events for that project (such as a release). 
%We refer to these occurrences in the discussion which follows.

\begin{figure}[t]
\centering
\subfloat[MySQL 3.23]{
\includegraphics[width=\textwidth]{figures/mysql-timeline.png}
\label{fig:mysql-timeline}				 
}

\subfloat[MaxDB 7.500]{					
\includegraphics[width=\textwidth]{figures/maxdb-timeline.png}
\label{fig:maxdb-timeline}
}

\subfloat[PostgreSQL 7.2]{					
\includegraphics[width=\textwidth]{figures/pgsql-timeline}
\label{fig:pgsql-timeline}
}
	\caption[]{NFR label per period. Each cell represents a 30-day period. %Numbers represent number of topics in that period labelled with that NFR. 
	Grid cell intensity (saturation) is mapped to label frequency
	relative to the largest label count of \emph{all} NFRs. Grey
	histogram bars indicate label frequency relative to that
	particular NFR's largest label count. Dashed vertical lines
	relate a project milestone (\emph{*Key events*}) to our topic windows. 
% \todo[inline]{better discussion}
}
\label{fig:timelines}
% Timelines created using src/validate/summary_labels.py
\end{figure}

@@

\subsection{Do Projects Differ in their Relative  Topic Interest?}
%\subsubsection{Do  projects differ in their relative  topic interest?}
%\noindent\textbf{2. Do  projects differ in their relative  topic interest?} ---
Yes. MySQL 3.23 had proportionally more
topics labelled \emph{functionality}, while MaxDB had proportionally more
\emph{efficiency} related topics. MaxDB was a very mature release ``donated'' to the open-source community, 
whereas MySQL was in its relative infancy, and	
security problems were more common (security is a component of \emph{functionality} in the ISO9126 model). 
In both cases \emph{portability} was a constant maintenance concern and was prevalent throughout the lifetime of the projects. It may surprise developers
how often portability arises as a concern.
%On one hand, this analysis is unsurprising; on the other hand, it provides confirmation that our approach identifies actual patterns.
%\subsection{Summary}

@@

\subsection{Summary of Techniques}
While an unsupervised technique such as LDA is appealing in its lack of human intervention, and thus lower effort, 
supervised learners have the advantage of domain knowledge, which typically means improved results. 
% NEIL - we got criticized for making it sound like this is the obvious thing to do... and then why do you need a learner?
%Our manual annotations were fairly quick to do, taking only a few minutes per 30 day period. 
Creating annotated topics (i.e., manual labels) for training is painstaking, but with a suitably representative set of topics, the effort is acceptable. To
annotate \emph{all} topics took us approximately 20 hours per project, but we estimate only 10\% of the topics need annotation to produce useful results.

@@
